---
title: "Developing Data Products Project Presentation"
author: "Stefan D. Huebner"
date: "1/16/2020"
output: 
  ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is for Coursera's Developing Data Products Course Project. You can use a slider to choose a maximum and minimum population and on a map the countries within that range will be highlighted. You can also hover over a country to see more detailed information.

App Link: https://tarski.shinyapps.io/DevelopingDataProductsProject/

GitHub Link: https://github.com/stefandh/DevelopingDataProductsProject

## ui.R Code

<style>
slides > slide {
  overflow-x: auto !important;
  overflow-y: auto !important;
}
</style>

```{r, echo = TRUE, eval = FALSE}
# load shiny
library(shiny)

# define UI for application
shinyUI(fluidPage(
    titlePanel("Population of Countries"),
    sidebarLayout(
        sidebarPanel(
            h3("Pick a Population Range"),
            h4("Use the slider to choose a maximum and minimum population 
               and the countries within that range will be highlighted. 
               You can hover over a country to see more detailed information."),
            sliderInput("population",
                        "people",
                        min = 0,
                        max = 1400000000,
                        value = c(0, 1400000000)),
        ),
        
        
        mainPanel(
            htmlOutput("plot1")
        )
    )
))
```

## server.R Code

<style>
slides > slide {
  overflow-x: auto !important;
  overflow-y: auto !important;
}
</style>

```{r, echo = TRUE, eval = FALSE}
# load required packages and data
library(shiny)
library(dplyr)
suppressPackageStartupMessages(library(googleVis))
data(Population)

# build dataframe for creating plot
countries <- data.frame(Population$Country, Population$Population,
                        hover = paste0(Population$Country, ": ",
                                       formatC(Population$Population, big.mark = ","), " people ",
                                       "(Rank ", Population$Rank, ")", "; ",
                                       Population$`% of World Population`*100, "% of World Population"),
                        check.names = FALSE)
countries$hover <- as.character(countries$hover)

# define server logic required to draw the plot
shinyServer(function(input, output) {
    
    output$plot1 <- renderGvis({
        
        # rename slider values
        minpop <- input$population[1]
        maxpop <- input$population[2]
        
        # filter data using slider input
        plotdata <- countries %>% 
            filter(Population$Population>minpop, Population$Population<maxpop)
        
        # plot map
        gvisGeoChart(plotdata, 
                     locationvar="Population$Country", hovervar="hover",
                     options=list(width=800, height=600))
        
    })
    
})
```

## Example Output
```{r}
suppressPackageStartupMessages(library(shiny))
suppressPackageStartupMessages(library(dplyr))
suppressMessages(suppressWarnings(suppressPackageStartupMessages(library(googleVis))))
data(Population)

countries <- data.frame(Population$Country, Population$Population,
                        hover = paste0(Population$Country, ": ",
                                       formatC(Population$Population, big.mark = ","), " people ",
                                       "(Rank ", Population$Rank, ")", "; ",
                                       Population$`% of World Population`*100, "% of World Population"),
                        check.names = FALSE)
countries$hover <- as.character(countries$hover)

shinyApp(
  
  ui = fluidPage(
    titlePanel("Population of Countries"),
    sidebarLayout(
        sidebarPanel(
            h3("Pick a Population Range"),
            h4("Use the slider to choose a maximum and minimum population 
               and the countries within that range will be highlighted. 
               You can hover over a country to see more detailed information."),
            sliderInput("population",
                        "people",
                        min = 0,
                        max = 1400000000,
                        value = c(0, 1400000000)),
        ),
        mainPanel(
            htmlOutput("plot1")
        )
    )
  ),
  
  server = function(input,output) {
    output$plot1 <- renderGvis({
        minpop <- input$population[1]
        maxpop <- input$population[2]
        plotdata <- countries %>% 
            filter(Population$Population>minpop, Population$Population<maxpop)
        gvisGeoChart(plotdata, 
                     locationvar="Population$Country", hovervar="hover")
    })
    
  },
  
  options = list(height = 500)
  
)
```